SMASH companion source code repository

### 2021-06-07 analysis/index.Rmd
workflowr::wflow_publish("index.Rmd")

> Zhengrong Xing, Peter Carbonetto and Matthew Stephens (2020).
> *Flexible signal denoising via flexible empirical Bayes shrinkage.*
> [arXiv:1605.07787][smash-preprint].

@@

[smash-github]: https://github.com/stephenslab/smash-paper
[smashr]: https://github.com/stephenslab/smashr
[smash-preprint]: https://arxiv.org/abs/1605.07787
[issues]: https://github.com/stephenslab/smash-paper/issues
[mit-license]: https://opensource.org/licenses/mit-license.html
[wavelab]: http://statweb.stanford.edu/~wavelab
[waveden]: http://www-ljk.imag.fr/SMS/software/GaussianWaveDen/down.html
[zhengrong]: https://github.com/zrxing
[peter]: http://pcarbo.github.io
[matthew]: http://stephenslab.uchicago.edu

>>>>

> Zhengrong Xing, Peter Carbonetto and Matthew Stephens (2021).
> [Flexible signal denoising via flexible empirical Bayes shrinkage.][smash-jmlr]
> *Journal of Machine Learning Research* 22(93), 1-28.

@@

[smash-github]: https://github.com/stephenslab/smash-paper
[smashr]: https://github.com/stephenslab/smashr
[smash-jmlr]: https://jmlr.org/papers/v22/19-042.html
[issues]: https://github.com/stephenslab/smash-paper/issues
[mit-license]: https://opensource.org/licenses/mit-license.html
[wavelab]: http://statweb.stanford.edu/~wavelab
[waveden]: http://www-ljk.imag.fr/SMS/software/GaussianWaveDen/down.html
[zhengrong]: https://github.com/zrxing
[peter]: http://pcarbo.github.io
[matthew]: http://stephenslab.uchicago.edu
